---
title: "Estimation strategy"
author: "Sumit Meghlani 64801343"
date: "3/25/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tibble)
library(dplyr)
library(FactoMineR)
library(caret)
library(plm)
source('functions.R')
```







## loading in the dataset
```{r}
# load the data
bigdf <- read.csv('train.csv')

gtest <- noout(bigdf)
summary(is.na(gtest$site_eui))
summary(is.na(bigdf$site_eui))
# use this to omit na values
# bigdf <- na.omit(bigdf)
ntrain = nrow(bigdf)
df = bigdf[sample(nrow(bigdf),ntrain),]
# to use the full dataset
boxplot(gtest$site_eui)

# log transformation for floor_area
# going to use max of summer months [Apr - Sep], min of winter months [Oct - Mar]
```


```{r}
df <- transform(df=bigdf)
# ClassSplit the main df
commDf <- ClassSplit(df)[[1]] %>% medianImp()
resDf <- ClassSplit(df)[[2]] %>% medianImp()
```

### Main Model regression equation

**$e_{t,J} = \alpha_{t,J} + \beta_1 minavg_{t,J} + \beta_2 maxavg_{t,J} + \beta_3 ESA_{t,J} +\beta_4 yb_{t,J} +\beta_5 elev_{t,J}+\beta_6 floar_{t,J}+\beta_7 factyp_{t,J}+ \epsilon_{t,J}$**

# running fest
Fest is a package in R used for fixed effects estimation.

```{r}
#running fixest
#-- cant be used for predictions as standard errors harder to compute with fixed effects
festcomModel <- feols(site_eui~minavg+maxavg+energy_star_rating+facility_type|Year_Factor+State_Factor|avg_temp~cooling_degree_days+heating_degree_days+precipitation_inches+days_above_110F+days_below_30F,commDf)

festresModel <- feols(site_eui~+minavg+maxavg+energy_star_rating+facility_type|Year_Factor+State_Factor|avg_temp~cooling_degree_days+heating_degree_days+precipitation_inches+days_above_110F+days_below_30F,resDf)

summary(festcomModel)
summary(festresModel)
```

```{r}
# - plotting density predictions
plot_results(commDf,festcomModel)
plot_results(resDf,festresModel)
```

# interval score implementation
```{r}
# running models to predict
PredfestcomModel <- feols(site_eui~minavg+maxavg+energy_star_rating+facility_type+Year_Factor+State_Factor|avg_temp~cooling_degree_days+heating_degree_days+precipitation_inches+days_above_110F+days_below_30F,commDf)

PredfestresModel <- feols(site_eui~+minavg+maxavg+energy_star_rating+facility_type+Year_Factor+State_Factor+cooling_degree_days+heating_degree_days+precipitation_inches+days_above_110F+days_below_30F,resDf)

```

```{r}

predMod <- plm(site_eui~minavg+maxavg+energy_star_rating+facility_type+floor_area,index=c('State_Factor'),data=commDf,model="within")

predict.out.plm(predMod,commDf)
```


```{r}
# 0.5 predictions
comModel50 <- probCheck(PredfestcomModel,commDf,0.51) 
resModel50 <- probCheck(PredfestresModel,resDf,0.51) 
#0.8 predictions
comModel80 <- probCheck(PredfestcomModel,commDf,0.95)
resModel80 <- probCheck(PredfestresModel,resDf,0.95)

REcomreg <- rbind(comModel50$summary,comModel80$summary)
colnames(REcomreg)=c("level","avgleng","IS","cover")
print(REcomreg)
REresreg <- rbind(resModel50$summary,resModel80$summary)
colnames(REresreg)=c("level","avgleng","IS","cover")
print(REresreg)
```





```{r residential feeffects echo=FALSE}
# running fixed effects one by one
feList = list()
all_FEs = c("State_Factor","Year_Factor")
for (i in 0:2){
  feList[[i+1]] <- feols(log(site_eui)~+minavg+maxavg+energy_star_rating+year_built+ELEVATION+floor_area+i(facility_type)+avg_temp,resDf,fixef = all_FEs[0:i])
}
etable(feList,title='Residential Regression Table')

cm <- c('(Intercept)'='Intercept','minavg'='Minimum Average (F)','maxavg'='Maximum Average(F)','energy_star_rating'='Energy Star Rating','year_built'='Year Built','floor_area'='Floor Area','avg_temp'='Average Temp (aux)')
tb <- modelsummary::modelsummary(feList,output="kableExtra",stars=TRUE,title = 'Regression Table',coef_map = cm,gof_omit = "BIC|Log.Lik.|R2 Adj.|R2 Within| R2 Pseudo|AIC")

```

#crossValidation
```{r}
crossValidationCont(bigdf,5,nperfmeas = 4,seed=12)
```

#Principal Component Analysis
Cannot do PRincipal Componenet Analysis for the life of me, if someone figures this out. Thanks in advance.
```{r}
library(factoextra)

encode_ordinal <- function(x, order = unique(x)) {
  x <- as.numeric(factor(x, levels = order, exclude = NULL))
  x
}
testDf <- bigdf %>% select(-c('site_eui','id','State_Factor','facility_type'))
testDf <- data.frame(lapply(testDf, function(x) scale(x, center = FALSE, scale = max(x, na.rm = TRUE)/100)))
testDf$facility_type <- encode_ordinal(bigdf$facility_type)
testDf$building_class <- encode_ordinal(testDf$building_class)


testDf$State_Factor <- encode_ordinal(bigdf$State_Factor)

ted.pca <- prcomp(na.omit(testDf))
fviz_eig(ted.pca)
groups <- as.factor(bigdf$State_Factor[1:11309])
fviz_pca_ind(ted.pca,
             col.ind = groups, # Color by the quality of representation
             palette = "Blues",
             addEllipses = TRUE, # Concentration ellipses
             ellipse.type = "confidence",
             legend.title = "Groups",
             repel = TRUE
             )
fviz_pca_var(ted.pca,
             col.var = "contrib", # Color by contributions to the PC
             gradient.cols = c("#00AFBB", "#FFC300", "#581845"),
             repel = TRUE     # Avoid text overlapping
             )
#test <- tibble(commDf$facility_type)
#princomp(na.omit(commDf[,3]),na.action=na.exclude, cor = TRUE)
#testmfa = MFA(base=test,group=c(54),type = c("n"),ncp=5,name.group = c("facility_type"))
eigs <- ted.pca$sdev^2
varTest <- rbind(
  SD = sqrt(eigs),
  Proportion = eigs/sum(eigs),
  Cumulative = cumsum(eigs)/sum(eigs))
varTest
```

```{r}
fviz_pca_biplot(ted.pca, repel = TRUE,
                col.var = "#2E9FDF", # Variables color
                col.ind = "#696969"  # Individuals color
                )
```


```{r}
causalmodel <- function(df){
    X <- df %>% select(-c('id','Year_Factor','State_Factor','facility_type'))%>% mutate_if(is.character,as.numeric) %>% mutate_all(~. -mean(.,na.rm=TRUE))
  X$State_Factor = df$State_Factor
  X$Year_Factor = df$Year_Factor
  X$facility_type = df$facility_type

# auxillary
  Xaux <- lm(avg_temp~cooling_degree_days*days_above_110F+heating_degree_days*days_below_30F+precipitation_inches,X)
  X$avg_temp <- predict(Xaux,X)
  X <- X %>% select(-c("cooling_degree_days","days_above_110F","heating_degree_days","days_below_30F","precipitation_inches"))

  Xmod <- lm(site_eui~minavg+maxavg+energy_star_rating+facility_type+floor_area+State_Factor+Year_Factor+avg_temp,X)
  return(Xmod)
}

```


```{r}
X <- commDf %>% select(-c('id','Year_Factor','State_Factor','facility_type'))#%>% #mutate_if(is.character,as.numeric) %>% mutate_all(~. -mean(.,na.rm=TRUE))
X$State_Factor = commDf$State_Factor
X$Year_Factor = commDf$Year_Factor
X$facility_type = commDf$facility_type

# auxillary
Xaux <- lm(avg_temp~cooling_degree_days*days_above_110F+heating_degree_days*days_below_30F+precipitation_inches,X)
X$avg_temp <- predict(Xaux,X)
X <- X %>% select(-c("cooling_degree_days","days_above_110F","heating_degree_days","days_below_30F","precipitation_inches"))

Xmod <- lm(site_eui~minavg+maxavg+energy_star_rating+facility_type+floor_area+State_Factor+Year_Factor+avg_temp,X)
xprob <- predict(Xmod,X,interval='prediction',level=0.5)

```

# see below the residential coefs plot



```{r residential coefficient estimate plots}
plotDf <- sort(resfestModel$coefficients)
qplot(x=plotDf,y = names(plotDf))+geom_bar(stat="identity", position="dodge")+labs(title='Residential Regression Coefficients',x = '%',y='Features')
```

```{r commercial fest for loop echo=FALSE}
feList = list()
all_FEs = c("State_Factor","Year_Factor")
for (i in 0:2){
  feList[[i+1]] <- feols(log(site_eui)~+minavg+maxavg+energy_star_rating+year_built+ELEVATION+floor_area+i(facility_type)+avg_temp,commDf,fixef = all_FEs[0:i])
}
etable(feList,drop='=',tex=TRUE,title='Commercial Regression Table')
```
Models to run interval score on
- festModel
- resfestModel
```{r}

plot(density(predict(festModel,commDf)))
lines(density(log(commDf$site_eui)),col=2,type='h')
```




